true

### 2020-04-27 analysis/robinson2020.Rmd
getting travis working
added nass back in

if (params$clean) {
  unlink(here::here("analysis/robinson2020.pdf"))
  unlink(here::here("analysis/robinson2020_cache"), recursive = TRUE)
  unlink(here::here("analysis/figures/."), recursive = TRUE)
  # unlink(here::here("analysis/data/derived_data/."), recursive = TRUE)
}
```

@@

```{r treering-spds, results = 'hide'}

gc()
gc()

@@

>>>>

if (params$clean) {
  unlink(here::here("analysis/robinson2020.pdf"))
  unlink(here::here("analysis/robinson2020_cache"), recursive = TRUE)
  unlink(here::here("analysis/figures/."), recursive = TRUE)
}
```

@@

```{r treering-spds, results = 'hide'}
gc()
gc()

@@

```{r gc2, echo = FALSE, message = FALSE, results='hide'}
gc()
gc()
```
